Initial Analysis

### 2020-07-15 Scripts/Initial_Analysis.Rmd
Fix typo on benthopelagic figure 3

Raw_Species_Data <- Tresholded_T_Data %>% 
  group_by(taxon_key) %>% 
  summarise(n_trans_spp = length(unique(fishing_entity))) %>% 
  left_join(Exploited_Species) %>%
  rename(scientific_name = taxon_name) %>% 
  left_join(Species_environ_list) %>%
  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",
                              ifelse(DemersPelag %in% c("bathypelagic","benthopelagic"), "bathy-bento-pelagic",paste(DemersPelag)
                              )
  ),
  n_trans_spp = ifelse(n_trans_spp > 100, 100, n_trans_spp),
  DemersPelag = str_to_title(DemersPelag)
  ) %>% 
  select(individual=scientific_name,
         value = n_trans_spp,
         group = DemersPelag) %>% 
  arrange(group,value)  %>% 
  mutate(
    individual = ifelse(individual == "Chloroscombrus chrysurus", "C. chrysurus",
                        ifelse(individual == "Scomberomorus commerson", "S. commerson",
                               individual)
    )
  ) %>% 
  filter(!group %in% c("Bathydemersal","Pelagic"))

>>>>

Raw_Species_Data <- Tresholded_T_Data %>% 
  group_by(taxon_key) %>% 
  summarise(n_trans_spp = length(unique(fishing_entity))) %>% 
  left_join(Exploited_Species) %>%
  rename(scientific_name = taxon_name) %>% 
  left_join(Species_environ_list) %>%
  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",
                              ifelse(DemersPelag %in% c("bathypelagic","benthopelagic"), "bathy-bentho-pelagic",paste(DemersPelag)
                              )
  ),
  n_trans_spp = ifelse(n_trans_spp > 100, 100, n_trans_spp),
  DemersPelag = str_to_title(DemersPelag)
  ) %>% 
  select(individual=scientific_name,
         value = n_trans_spp,
         group = DemersPelag) %>% 
  arrange(group,value)  %>% 
  mutate(
    individual = ifelse(individual == "Chloroscombrus chrysurus", "C. chrysurus",
                        ifelse(individual == "Scomberomorus commerson", "S. commerson",
                               individual)
    )
  ) %>% 
  filter(!group %in% c("Bathydemersal","Pelagic"))
